A thesis draft

### 2018-11-16 res/sections/08-Background.tex
Fix grammar

\subsection{OpenFlow protocol}
The SDN strategy is often associated with OpenFlow protocol: this communication
protocol aims is to give access to the forwarding network component to the lower
layer network infrastructure, made of switches and routers. OpenFlow enables
the remote administration of networks working on layer 3: packets forwarding
tables can be modified relying on packet matching rules. Following this
approach it is possible to change routes periodically or ad-hoc, based on
packet types, traffic or network load.

>>>>

\subsection{OpenFlow protocol}
The SDN strategy is often associated with the OpenFlow protocol: this 
communication protocol aims is to give access to the forwarding network 
component to the lower layer network infrastructure, made of switches and 
routers. OpenFlow enables the remote administration of networks working on 
layer 3: packets forwarding tables can be modified relying on packet matching 
rules. Following this approach it is possible to change routes periodically or 
ad-hoc, based on packet types, traffic or network load.
